\vspace{-5mm} \fontsize{24pt}{12pt}\selectfont \textbf{What's so Special about Philosophy?}

### 2015-10-27 writeup/draft.tex
raggedbottom option for easier reading
footnote with no markers added
3cycles graph updated

% ------
% Maketitle metadata
\title{\vspace{-5mm}%
	\fontsize{24pt}{12pt}\selectfont
	\textbf{What's so Special About Philosophy?} 
	}	
\author{%
\fontsize{14pt}{14pt}\selectfont
	Unraveling Wikipedia's First Link Network \vspace{-2mm}\\
	}
\date{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle
\thispagestyle{fancy}
%========================ABSTRACT====================================

@@

Apples, oranges, and the most obscure Dylan song too---is everything a few clicks from Philosophy? 
Within Wikipedia, the surprising answer is yes: nearly all 
paths\footnote{
nearly $99.6\%$ of First Link paths, ending inside Wikipedia, lead to the Philosophy article (see traversal funnels discussion for details).}
\footnote{
An analysis performed in 2011 by Mat Kelcey posted on his blog (and a smiliar post by Ilmari Karonen) suggest $94.5\%$ of articles end up at Philosophy.
}
lead to Philosophy.
Wikipedia is the largest, most meticulously indexed collection of human knowledge ever amassed. 
\footnote{
cite MIT Tech Review Article: http://www.technologyreview.com/featuredstory/520446/the-decline-of-wikipedia/
}
More than information about a topic though, Wikipedia is a marvelous web of naturally emerging relationships.  
By following the First Link in an article, we connect entries to form a directed network within Wikipedia: Wikipedia's First Link Network. 
Here we study the English edition of Wikipedia's First Link Network for insight into how we relate topics, ideas, people, objects, and events.

@@

\begin{figure}[H]
\centering
\caption{highest ranking 2-Cycles}
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{graphics/2_cycles.pdf}
    \end{subfigure}
\end{figure}

@@

\begin{figure}[H]
\centering
\caption{highest ranking 3-Cycles}
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{graphics/3_cycles.pdf}
    \end{subfigure}
\end{figure}

@@

- thank you to my friend RJ for pointing out the xkcdc comic about links to Philosophy

>>>>

% ------
% Maketitle metadata
\title{\vspace{-5mm}%
	\fontsize{24pt}{12pt}\selectfont
	\textbf{What's so Special about Philosophy?} 
	}	
\author{%
\fontsize{14pt}{14pt}\selectfont
	Unraveling Wikipedia's First Link Network \vspace{-2mm}\\
	}
\date{}

@@

%text, figure spacing
\raggedbottom

%footnote withou marker
\newcommand\blfootnote[1]{%
  \begingroup
    \renewcommand\thefootnote{}\footnote{#1}%
      \addtocounter{footnote}{-1}%
   \endgroup }
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle
\thispagestyle{fancy}
%========================ABSTRACT====================================

@@

Apples, oranges, and the most obscure Dylan song too---is everything a few clicks from Philosophy? 
Within Wikipedia, the surprising answer is yes: nearly all 
paths lead to Philosophy.
\footnote{
nearly $99.6\%$ of First Link paths, ending inside Wikipedia, lead to the Philosophy article (see traversal funnels discussion for details).}
\footnote{
An analysis performed in 2011 by Mat Kelcey posted on his blog (and a smiliar post by Ilmari Karonen) suggest $94.5\%$ of articles end up at Philosophy.
}
Wikipedia is the largest, most meticulously indexed collection of human knowledge ever amassed. 
\footnote{
cite MIT Tech Review Article: http://www.technologyreview.com/featuredstory/520446/the-decline-of-wikipedia/
}
More than information about a topic though, Wikipedia is a marvelous web of naturally emerging relationships.  
By following the First Link in an article, we connect entries to form a directed network within Wikipedia: Wikipedia's First Link Network. 
Here we study the English edition of Wikipedia's First Link Network for insight into how we relate topics, ideas, people, objects, and events.

@@

\begin{figure}[H]
\centering
\caption{highest ranking 2-cycles}
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{graphics/2_cycles.pdf}
    \end{subfigure}
\end{figure}

@@

\begin{figure}[H]
\centering
\caption{highest ranking 3-cycles}
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{graphics/3_cycles.pdf}
    \end{subfigure}
\end{figure}

@@

\blfootnote{
- thank you to my friend RJ for pointing out the xkcdc comic about links to Philosophy
}
